---
title: "Statistical Inference Course Project Part 1"
Author: Danielle
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE,fig.width=12, fig.height=8, fig.align='center', fig.path='Figs/')
```
Overview: 
In this Report we will investigate the exponential distribution in R and compare it with the Central Limit Theorem. The exponential distribution will be simulated in R with rexp(n, lambda) where lambda is the rate parameter. The mean of exponential distribution is 1/lambda and the standard deviation is also 1/lambda. Set lambda = 0.2 for all of the simulations. We will investigate the distribution of averages of 40 exponentials. We will need to do a thousand simulations.

## Simulation
n=40
lambda = 0.2
theoretical mean = 5
standard deviation = 5


1. Create a exponential distribution with 40 exponentials.
```{r}
set.seed(4000)
n <- 40
lam <- 0.2
sample <- rexp(n, lam)

```

2. Run a thousand simulations
```{r}
simulation = NULL
for (i in 1 : 1000) simulation = c(simulation, mean(rexp(n, lam)))
```

3. Histogram of the simulations
```{r}
hist(simulation,prob=TRUE, xlab = "Mean of 40 Exponentials", ylab = "Density")
```

## simulation mean vs theoretical mean
```{r}
sim_mean <- mean(simulation)

```
The simulation mean is `r sim_mean` is very close to the theoretical mean of 5.

## simulation variance vs theoretical variance
```{r}
sim_var <- var(simulation)
theo_var <- (1/lam)^2 /n
```
The simulation variance is `r sim_var` is very close to the theoretical variance of `r theo_var`.

## Distribution of simulation vs theoretical distribution
```{r}
hist(simulation,prob=TRUE, xlab = "Mean of 40 Exponentials", ylab = "Density"
     , main = "Comparison of simulation distribution vs theoretical distribution")
curve(dnorm(x, mean=mean(simulation), sd=sd(simulation)), add=TRUE, col="Blue", lwd = 2)
curve(dnorm(x, mean=5, sd=sqrt(theo_var)), add=TRUE, col="Red", lwd = 2)
legend('topright', c("simulation", "theoretical"), lty=c(1,2), col=c("black", "red"))
```
As shown in the graph above, the simulation will be approximated with the normal distribution

## Confidence intervals

The simulation confidence intervals is:
```{r}
sim_mean + c(-1,1) * qt(0.975, 39) * sqrt(sim_var) * sqrt(1/40)
```
The theoretical confidence intervals is:
```{r}
5 + c(-1,1) * qt(0.975, 39) * sqrt(theo_var) * sqrt(1/40)
```

## Conclusion
This exercise shown that, based on the central limit theorem, when the sample size is big enough, the sample distribution will be approximated with the normal distribution.

